Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
mise a jour resultats benchs
typos

There are many possible combinations of the above techniques, and it is not evident which ones perform more or less precisely or more or less efficiency on real-life examples. One needs to experiment. Unfortunately, the published literature on the subject lacks experimental comparative assessments. One purpose of this article is therefore to propose such experimental results.
\medskip

@@

We choose $P_R$ as the set of loop headers of the function, plus the initial
state. In this case, we have three elements in $P_R$.
We also unroll the loop once, in order to distinguish the paths that do not go
through the loop from the others:
\begin{lstlisting}[numbers=none]
if (wait) {
   while (wait()) {}
}
\end{lstlisting}

@@

For the computation of disjunctive invariants, we experimented with a heuristic
of dynamic construction of the $\sigma$ function, adapted from
\cite{DBLP:conf/pldi/GulwaniZ10}.  We start with one single
disjunct per control point ($m=1$), and we start with an empty map $\sigma$. We also
define a maximal bound on the number of disjunct per control point, noted $M$.
$\sigma(j,k)$ is then constructed on the fly only when needed.
When $\sigma(j,k)$ needs to be computed, we first compute the image of the
abstract value $X_k$ by the path indexed by $j$, and try to find an existing
disjunct of index $k'$ so that the convex hull of the two abstract values is
exactly the union of them. If such an index exists, then $\sigma(j,k) = k'$.
Otherwise:
\begin{itemize}
	\item if $m < M$, we increase $m$ by $1$ and define $\sigma(j,k) = m$
	\item if $m = M$, we define $\sigma(j,k) = M$
\end{itemize}

@@

\begin{figure}[h]
  \MM{Y a-t-il moyen d'avoir un truc plus lisible en impression noir
    et blanc, genre des hachures ?}
  \begin{center}
    \input{./techniques.tex}
  \end{center} 
  \vspace{-20px}
  \caption{Comparison of the abstract values obtained by classical abstract
  interpretation (S), \emph{Guided Static
  Analysis} (G), \emph{Path-focused} technique (PF), our combined technique
  (G+PF), and its version with disjunctive invariants (DIS).}
  \label{fig:techniques}
\end {figure}

>>>>

There are many possible combinations of the above techniques, and it is not
evident which ones perform more or less precisely or more or less efficiently on real-life examples. One needs to experiment. Unfortunately, the published literature on the subject lacks experimental comparative assessments. One purpose of this article is therefore to propose such experimental results.
\medskip

@@

We choose $P_R$ as the set of loop headers of the function, plus the initial
state. In this case, we have three elements in $P_R$.
We also unroll the loop once, in order to distinguish the paths that do not go
through the loop from the others:
\begin{lstlisting}[numbers=none]
if (wait()) {
   while (wait()) {}
}
\end{lstlisting}

@@

For the computation of disjunctive invariants, we experimented with a heuristic
of dynamic construction of the $\sigma$ function, adapted from
\cite{DBLP:conf/pldi/GulwaniZ10}.  We start with one single
disjunct per control point ($m=1$), and we start with an empty map $\sigma$. We also
define a maximal bound on the number of disjunct per control point, noted $M$.
$\sigma(j,k)$ is then constructed on the fly only when needed.
When $\sigma(j,k)$ needs to be computed, we first compute the image of the
abstract value $X_k$ by the path indexed by $j$, and try to find an existing
disjunct of index $k'$ so that the least upper bound of the two abstract values is
exactly the union of them. If such an index exists, then $\sigma(j,k) = k'$.
Otherwise:
\begin{itemize}
	\item if $m < M$, we increase $m$ by $1$ and define $\sigma(j,k) = m$
	\item if $m = M$, we define $\sigma(j,k) = M$
\end{itemize}

@@

\begin{figure}[h]
  \begin{center}
    \input{./techniques.tex}
  \end{center} 
  \vspace{-20px}
  \caption{Comparison of the abstract values obtained by classical abstract
  interpretation (S), \emph{Guided Static
  Analysis} (G), \emph{Path-focused} technique (PF), our combined technique
  (G+PF), and its version with disjunctive invariants (DIS).}
  \label{fig:techniques}
\end {figure}
